---
title: "Bird species composition in coastal urban habitats"
output:
  bookdown::word_document2:
    reference_docx: "Para_Template.docx"
bibliography: tesis_ref_2020.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,	message = FALSE,warning = FALSE,cache = TRUE,comment = FALSE)

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)
library(ggrepel)
library(patchwork)
library(kableExtra)
library(knitr)
library(rasterVis)

```



```{r}
#preparacion de datos registro aves

AvesInv2 <- read_rds("AbundInv_Corregido.rds") 
AvesInv2 <-AvesInv2 %>% ungroup() %>% dplyr::select(-Sitio) %>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()

AvesPrim2 <- read_rds("AbundPrim_Corregido.rds")
AvesPrim2 <-AvesPrim2 %>% ungroup() %>% dplyr::select(-Sitio)%>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()

#Datos ambientales  incluidos buffers

Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
Amb <- Amb %>% 
  dplyr::select(Sitio,CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>% 
  rename( `Vegetation cover` =CobVeg) %>% rename( `Distance to river` =Distancia_rio) %>% 
  rename( `Native forest` =`Buffer_2200_Bosque Nativo`) %>% rename(Crops =`Buffer_2200_Cultivos`) %>% 
  rename( Gravel =`Buffer_2200_Grava`) %>% rename( Ocean =`Buffer_2200_Oceano`) %>% 
  rename( Grassland =`Buffer_2200_Pastizales`) %>% rename( `Shrublands` =`Buffer_2200_Matorrales`) %>% 
  rename( `Paved surface` =`Buffer_2200_Sup impermeables`) %>% rename( `Sand` =`Buffer_2200_Suelo arenoso`) %>% 
  rename( `Tree plantation` =`Buffer_2200_Plantación de árboles`) %>% 
  rename( Altitude = Altura)

rownames(Amb) <- Amb$Sitio

Amb <- Amb %>% dplyr::select(-Sitio) %>%
  mutate(AMBIENTE= str_replace(AMBIENTE, "URBANO", "Urban"),
         AMBIENTE= str_replace(AMBIENTE, "VERDE", "Green area"),
         AMBIENTE= str_replace(AMBIENTE, "ROCA INTERVENIDA", "Modified rocky shore"),
         AMBIENTE= str_replace(AMBIENTE, "PLAYA INTERVENIDA", "Urbanized beach"),
         AMBIENTE= str_replace(AMBIENTE, "ROCA NATURAL", "Natural rocky shore"),
         AMBIENTE= str_replace(AMBIENTE,"PLAYA NATURAL", "Natural beach"))
```


### Introduction

1. Establish importance of the field- provide background, keywords- present the problem

[Establish the importance of this research topic]

Urbanization has been growing rapidly. During 2018, more than half of world’s population  lived  in  urban  settlements.   
Cities are growing in both size and number, by  2018  the  number  of  cities  with  at  least  1  million  inhabitants  had  grown  to 548 [@UN_WorldCities2018].
and 

[Provide general background information]
Urban modification over natural environments is one of the mayor causes of species loss [@czech2000economic]. Some of these loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization]. This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biome [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].

[Establish the importance of this research topic, more specific/detailed way]
This urban homogenization is projected to lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
which has been studied mostly in birds and plants

[Provide general background information, more specific/detailed way]
Bird species communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments. However, local features seems to be important in those assembles.
Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
Rural birds
According to @clergeau2001urban, urban  bird  communities  are  independent of the bird diversity of adjacent landscapes, and that local features are more important than surrounding landscapes. 


2. Previous an current research and contributions

[Describe general problem area or the current research focus of the field]
Cities  in  coastal  areas  are the  most affected  by natural  and human  generated  disasters while  are  alsoattractive  for  private  investments, and often located in  ecologically  sensitive  areas.  Generally coasts  are  more  densely  populated compared toin-land areas due  to the many  keyeconomic  activities takingplace in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling. Coastal areas are also home to species and habitats that provide  many benefits  to  the  societybut  might  often  be  threatened.  Coastal  areas  biomes  are  rich  in biodiversity but at the same time extremely vulnerable.

By 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017]. many  key economic  activities taking place in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling.

coasta como area vulnerable y hay poca investigacion
, however urbanization has been mostly focus in terrestrial aspects.


[Provide transition between the general problem area and the literature review]
More than the half of the cities in the world are coastal cities and they lack of studies addressing marine and terrestrial interactions.

3. Locate the gap-describe the problem to address-present a prediction to be tested

[Provide brief overview of key research projects in this area]
Urban homogenization has been studied in cities, focused in terrestrial variables
Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats

[Describe gaps in the research]
There is a gap in studies that focus in coastal ecotone and the influence of urban areas
focusing on marine and terrestrial interaction of species in an urbanized area and how birds use this as habitats

[Describe paper itself]
This research aim to identified the use of coastal urban habitats by birds describing the composition of species in different environments, considering bird species origin (marine and terrestrial).
with the aim of: 1. Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2. identify how urbanization affects those bird assembles, 3. Evaluate iconic bird species habitat occupation, and 4. describe bird behavior in those habitats

4. Describe the present paper
[Give details about the methodology reported in the paper]
The present study was carried out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile

[Announces the findings]
Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inland bird species

### Methodology


```{r, results='hide'}
##### METAMDS: Non-metric Multidimensional scaling- NMDS

#########################################################
#Función para sacar los datos y ocupar ggplot
TidyNMDS <- function(MDS, COVS){
  DF <- COVS
  DF2 <- MDS$points %>% as.data.frame()
  DF <- bind_cols(DF2, DF)
  return(DF = DF)
}
#########################################################
#Invierno
Inv_nmds2_bray <- suppressMessages(metaMDS(AvesInv2, autotransform = FALSE, distance="bray", k=2, try=20, trymax=100,  wascores=FALSE, trace=1, plot=FALSE))
#Primavera
Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
```

1. Overview-purpose of the work-give source of material/equipment used

[General overview of this section]
In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on bird presence analysed using occupancy models and analysed bird assembles in those environment. 

[Provide background information and justification]
The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to Censo 2017). The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years. 
The area is near by the chilean capital, Santiago, which has more than 7 million inhabitants.
This area is immerse in a natural-rural matrix composed ... in a geographic Coastal mountain chain-- papers bahi concon y viña

[Provide an overview of the procedure/method itself]
To estimate species composition and assembles, occupancy models were developed with DiversityOcuppancy package [@divoccu] and 
species composition were analysed with the vegan package [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models. 
  
2. Details about materials and methods- justify choices

[Provide details about what was done and used and shows that care was taken]
Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1). 
Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019. Surveys were conducted randomly during sunrise and the three hours later for 10 minutes, registering species and behaviour.

Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites. We tested a model where seasonality has a interacttion with the habitats defined in this research.


[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
Bird commmunities were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with  DiversityOcuppancy package [@divoccu](see table 1).
We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).  To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.

In order to understand habitat use by birds, bird activities were counted by each habitat

Fit of environmental variables on species ordination was also tested. 


3. Relate to other studies

[Describe what was done by referring to existing mehods in the literature]
To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.

[Provide more detailed information about the method and show that was a good choice]
Covariables of detection and occupation are describedd in table 1.


4. Indicate where problems occurred

[Mention possible difficulty in the methodology]

```{r}
#figura 1 con los 6 ambientes costeros estudiados
```


```{r}
#Covariables de deteccion y ocupaciono ocupadas para los modelos
```



### Results

1. Revisting the research aim/existing research
Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.

2. General overview of results
The six coastal urban habitats shows distingible birs species assembles where only a few species contribute to the difference between them. For these habitats, bird assemblages differ between winter and spring seasons.
Environmental variables can be responsible of both community identities and use of habitat idiviualy


3. Invitations to view results

Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla 3). Distribution of sites in graphical NMDS (Fig. \@ref(fig:NMDS)) showedthat both seassons presented differences in abundance of species mostly in the inland sites. Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites. 

```{r NMDS, fig.width=9, fig.height=4, fig.cap="Sites distribution in A winter and B spring"}
#Funcion para grafico NMDS en ggplot Invierno
Tidy_Inv_nmds2_bray <- TidyNMDS(MDS = Inv_nmds2_bray, COVS = Amb)

Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
  ggtitle('A')

#Funcion para grafico NMDS en ggplot Primavera
Tidy_Prim_nmds2_bray <- TidyNMDS(MDS = Prim_nmds2_bray, COVS = Amb)

Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
  ggtitle('B')

#Ambos graficos con paquete patchwork
Inv+Prim + plot_layout(guides = 'collect')
```

Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different. There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig. \@ref(fig:ANOSIM))

```{r, results='hide'}
## test: ANOSIM

#Invierno
Diss_Inv2 <- vegdist(AvesInv2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
#con base de datos por abundancia
Anosim_Diss_Inv2<-anosim(Diss_Inv2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", strata = NULL, parallel = getOption("mc.cores"))
Summ_AnosimInv <-summary(Anosim_Diss_Inv2)

#Primavera
Diss_Prim2 <- vegdist(AvesPrim2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
#con base de datos por abundancia
Anosim_Diss_Prim2<-anosim(Diss_Prim2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray",strata = NULL, parallel = getOption("mc.cores")) 
summary(Anosim_Diss_Prim2)

```


```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A winter (R=0.584, P<0.001) and B spring (R=0.573, P< 0.001)"}
Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
  xlab("Variables")+ ylab("Dissimmilarity rank")+
  ggtitle('A')

Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
 xlab("Variables")+ ylab("Dissimmilarity rank")+
   ggtitle('B')

Inv / Prim
```


4. Specific/key results in details

Both sampled seasons showed that few species contribute to differences between habitats. Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.  (For a complete species list of SIMPER, see Suplementary material).


Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))

Species such as xxx, showed differernces in habitat use between seasons.
(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))


```{r OccuInv, fig.width=9.5, fig.height=6.5}
Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
Larus <-read_rds("PredInv_Larus_dominicanus.rds") 
Coragyps <-read_rds("PredInv_Coragyps_atratus.rds")
Larosterna <-read_rds("PredInv_Larosterna_inca.rds")
Leucophaeus <-read_rds("PredInv_Leucophaeus_modestus.rds")
Columba <-read_rds("PredInv_Columba_livia.rds")
Turdus <-read_rds("PredInv_Turdus_falcklandii.rds")
Sephanoides <-read_rds("PredInv_Sephanoides_sephaniodes.rds")

Especies <- stack(Pelecanus,Larus,Coragyps, Larosterna, Leucophaeus,  Columba, Turdus, Sephanoides)
names(Especies) <- c("Pelecanus thagus", "Larus dominicanus", "Coragyps atratus", "Larosterna inca", "Leucophaeus modestus", "Columba livia", "Turdus falcklandii", "Sephanoides sephaniodes")

Mytheme <- YlOrRdTheme()
Mytheme$panel.background$col <- "black"

levelplot(Especies, par.settings=Mytheme)


```


```{r OccuPrim, fig.width=7, fig.height=6.5}
Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
Columba <-read_rds("PredPrim_Columba_livia.rds")
Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
Pelecanus <-read_rds("PredPrim_Pelecanus_thagus.rds")

Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
names(Especies) <- c("Leucophaeus pipixcan", "Larus dominicanus", "Columba livia", "Larosterna inca", "Phalacrocorax bougainvillii", "Pelecanus thagus")

Mytheme <- YlOrRdTheme()
Mytheme$panel.background$col <- "black"

levelplot(Especies, par.settings=Mytheme)

```



During winter, community assemblages were explain by three environmental variables: coastal urban habitats, crops and tree plantations. 
In spring, variables were coastal urban habitats and native forest.


```{r}
#ORDISTEP

#Invierno
#Step: AvesInv2 ~ AMBIENTE + Cultivos + `Plantacion de arboles`

#Primavera
#Step: AvesPrim2 ~ AMBIENTE + `Bosque nativo` 

```

species for each habitat
Occupancy model map show


```{r}
#Resultados occupancia para especies dde Simper
ModelosOccuPrim <- read_rds("ModelosOccuPrim_Ms.rds")
#Para generar las ecuaciones **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**
```


Finally, use of these habitats can be seen with the activity record of bird species.

```{r Comportamineto, fig.height=10}
ComportamientoInv <- read_rds("ComportamientoInv.rds")
I <-ggplot(ComportamientoInv) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")

P <-ggplot(ComportamientoPrim) + 
  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")

I/P
  
```





5. Comparisons with results in other research

Occupancy models for specific species 



6. problems with results

7. Possible implications with results






### Discussion/Conclusion

1. Revising previous research- summaries
[Revisit previous research]
[Revisit Introduction to recall specific weakness in methodology used in previous studies]

2. Mapping 
[Revisit methodology used in this study]
[Revisit and summaries the results]
[Show where and how the present work fits into the research "map" in this field]

3. Achievements/contributions- refining implications
[Recall an aspect of the results that represents a positive achievement or contribution of this work]
[Focus in the meaning and implications of the achievements in this work]
[Note if one of the achievement or contributions of the work is a novelty]
[Describe implications of the results, including possible applications]

4. Limitations-current and future work-applications
[Describe limitations which should direct future research]
[Suggest a specific area to be addressed in future work]


















### References