---
title: "Ms Habitat aves"
author: "Giorgia Graells"
date: "`r Sys.Date()`"
output:
  word_document: default
  ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,	message = FALSE,warning = FALSE,cache = TRUE,comment = FALSE)

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)
library(ggrepel)
library(patchwork)
library(kableExtra)

```


```{r}
#preparacion de datos registro aves

AvesInv2 <- read_rds("AbundInv_Corregido.rds") 
AvesInv2 <-AvesInv2 %>% ungroup() %>% dplyr::select(-Sitio) %>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()

AvesPrim2 <- read_rds("AbundPrim_Corregido.rds")
AvesPrim2 <-AvesPrim2 %>% ungroup() %>% dplyr::select(-Sitio)%>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()

#Datos ambientales  incluidos buffers

Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
Amb <- Amb %>% 
  dplyr::select(Sitio,CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>% 
  rename( `Vegetation cover` =CobVeg) %>% rename( `Distance to river` =Distancia_rio) %>% 
  rename( `Native forest` =`Buffer_2200_Bosque Nativo`) %>% rename(Crops =`Buffer_2200_Cultivos`) %>% 
  rename( Gravel =`Buffer_2200_Grava`) %>% rename( Ocean =`Buffer_2200_Oceano`) %>% 
  rename( Grassland =`Buffer_2200_Pastizales`) %>% rename( `Shrublands` =`Buffer_2200_Matorrales`) %>% 
  rename( `Paved surface` =`Buffer_2200_Sup impermeables`) %>% rename( `Sand` =`Buffer_2200_Suelo arenoso`) %>% 
  rename( `Tree plantation` =`Buffer_2200_Plantación de árboles`) %>% 
  rename( Altitude = Altura)

rownames(Amb) <- Amb$Sitio

Amb <- Amb %>% dplyr::select(-Sitio)
```




#### Introduction

1. Establish importance of the fild- provide background, keywords- present the problem

[Stablish the importance of this research topic]
Urbanization have been one of the mayor causes of species loss

[Provide general background information]
Urban areas presents species homogenization  

[Stablish the importance of this research topic, more specific/detailed way]
Urban homogenization represents...

[Provide general background information, more specific/detailed way]

2. Previous an current research and contributions

[Describe general problem area or the current research focus of the field]
Birds have been studied un urban areas and show this phenomena

[Provide transition between the general problem area and the literature review]
Birs comunities in urban areas depend of the perurban composition of species

3. Locate the gap-describe the proble to address-present a prediction to be tested

[Provide brief overview of key research projects in this area]
More than the half of the cities in the world are coastal cities and they lack of studies addressing marine. terrestrial interactions.

[Describe gaps in the research]
However there is a gap in studies that focus in coastal ecotone and the influence of antrhopized areas

[Decribe paper itself]
This research describe ...
with the aim of: 1. Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2. identify how urbanization affects those bird assembles, 3. Evaluate iconic bird species habitat ocupation, and 4. describe bird behavior in those habitats


4. Describe the present paper
[Give details about the methodology reported in the paper]
Bird surveys were carry out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile

[Announces the findings]





#### Metodology

1. Overview-purpose of the work-give source of material/equipment used

[General overview of this section]
In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area that includes three municipalities in central Chile.

[Provide background information and justification]
Coastal environments were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1)


[Provide an overview of the procedure/method itself]
Bird surveys were conducted in each sample site twice (winter (junio-jul) and spring (nov-dec)), 2019 given migratory species en this area, during sunrise and the three hours later for 10 minutes. 
The total of birds seing and heard was registred, in addition with the position and behavior of the bird or group of birds observed.

A characterization of environments were made throgh vegetational cover measurement and an spatial characterization with landcover information.

2. Details about materials and methods- justify choices

[Provide details about what was done and used and shows that care was taken]

Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites. We tested a model where seasonality has a interacttion with the habitats defined in this research .

To analyse the data, we used occupancy modeling to provide information about bird habitat use.
Occupancy variables
Detection variables
Seasonal variables


[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
To compare bird commmunities and species identity in them, we used ordination methods with vegan package in R with species abundances corrected by occupancy.
We tested significant differences among environments with an analysis of similarities (ANOSIM) 

To determine species contribution to the differrence between environments we used Bray-Curtis dissimilaries with SIMPER analysis.


3. Relate to other studies

[Describe what was done by referring to existing mehods in the literature]

[Provide more detailed information about the method and show that was a good choice]
Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models

4. Indicate where problems occurred

[Mention possible difficulty in the methodology]






**Poner en paper**

1. Hacer una descripcion del ensamble de especies (unidas las temporadas) y representar con un NMDS, ANOSIM y SIMPER.
Se utilizó las abundancias corregidas por ocupancia, lo que se obtiene corriendo los modelos de ocupancia para cada especie.





Mostrar la comparacioón entre natural y urbano.
Sumar Envfit

2. Realizar un mapa dde probabilidad de presencia para especies icónicas 1-100%

3. Grafficar las barras de comportamiento para las mismas espcies icónicas




### Results

1. Revisting the research aim/existing research

2. General overview of results
A partir del nmds

El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia

```{r tabla1}
#Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0


```


3. Invitations to view results
variabilidad entre ambientes segun anosim

4. Specific/key results in details
que contribuye mas al cambio
que determina las diferencias

5. Comparisons with results in other research

6. problems with results

7. Possible impllications with results






### Discussion/Conclusion

1. Revisting previous research- summarise
[Revisit previous research]
[Revisit Introduction to recall specific weakness in methodology used in previous studies]

2. Mapping 
[Revisit methodology used in this study]
[Revisit and summarise the results]
[Show where and how the present work fits into the research "map" in this field]

3. Achivements/contributions- refining implications
[Recall an aspect of the results that represents a postitive achievement or contribution of this work]
[Focus in the meaning and implications of the achievements in this work]
[Note if one of the achievement or contributions of the work is a novelty]
[Describe implications of the results, including possible applications]

4. Limitations-current and future work-applications
[Describe limitations which should direct future research]
[Suggest a specific area to be addressed in future work]


```{r, results='hide'}
##### METAMDS: Non-metric Multidimensional scaling- NMDS

#########################################################
#Función para sacar los datos y ocupar ggplot
TidyNMDS <- function(MDS, COVS){
  DF <- COVS
  DF2 <- MDS$points %>% as.data.frame()
  DF <- bind_cols(DF2, DF)
  return(DF = DF)
}
#########################################################
#Invierno
Inv_nmds2_bray <- suppressMessages(metaMDS(AvesInv2, autotransform = FALSE, distance="bray", k=2, try=20, trymax=100,  wascores=FALSE, trace=1, plot=FALSE))
#Primavera
Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
```


```{r, fig.width=9, fig.height=4}
#Funcion para grafico NMDS en ggplot Invierno
Tidy_Inv_nmds2_bray <- TidyNMDS(MDS = Inv_nmds2_bray, COVS = Amb)

Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area") , values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
  ggtitle('A')

#Funcion para grafico NMDS en ggplot Primavera
Tidy_Prim_nmds2_bray <- TidyNMDS(MDS = Prim_nmds2_bray, COVS = Amb)

Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"), values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
  ggtitle('B')

#Ambos graficos con patchwork
Inv+Prim + plot_layout(guides = 'collect')
```

```{r, results='hide'}
## test: ANOSIM

#Invierno
Diss_Inv2 <- vegdist(AvesInv2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
#con base de datos por abundancia
Anosim_Diss_Inv2<-anosim(Diss_Inv2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", strata = NULL, parallel = getOption("mc.cores"))
Summ_AnosimInv <-summary(Anosim_Diss_Inv2)

#Primavera
Diss_Prim2 <- vegdist(AvesPrim2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
#con base de datos por abundancia
Anosim_Diss_Prim2<-anosim(Diss_Prim2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray",strata = NULL, parallel = getOption("mc.cores")) 
summary(Anosim_Diss_Prim2)

```


```{r, fig.width=9}
Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
  xlab("Variables")+ ylab("Dissimmilarity rank")+
  ggtitle('A')

Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
 xlab("Variables")+ ylab("Dissimmilarity rank")+
   ggtitle('B')

Inv / Prim
```




```{r, results='hide'}
##### ENVFIT: Fits an Environmental Vector or Factor onto an Ordination
###################################################
TidyEnvFit <- function(ENVFit, alpha = 0.05){
  DF <- ENVFit$vectors$arrows %>% as.data.frame()
  DF$Factor <- rownames(DF)
  DF$Pval <-ENVFit$vectors$pvals
  DF <- DF %>% dplyr::filter(Pval < alpha)
  return(DF = DF)
}
###################################################
EnvfitInv2 <- envfit(Inv_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation` , data=Amb, perm=9999)
Tidy_EnvfitInv2 <- TidyEnvFit(EnvfitInv2)

EnvfitPrim2 <- envfit(Prim_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation`, data=Amb, perm=9999)
Tidy_EnvfitPrim2 <- TidyEnvFit(EnvfitPrim2)
```


```{r,  fig.width=9, fig.height=4}
Inv <- ggplot(Tidy_Inv_nmds2_bray)+
  geom_segment(data=Tidy_EnvfitInv2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
  geom_text_repel(data=Tidy_EnvfitInv2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
  
  theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
  ggtitle('A')

Prim <- ggplot(Tidy_Prim_nmds2_bray)+
  geom_segment(data=Tidy_EnvfitPrim2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
  geom_text_repel(data=Tidy_EnvfitPrim2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
    theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
  ggtitle('B')

Inv+Prim + plot_layout(guides = 'collect')

```








### References