---
title: "Ms Habitat aves"
author: "Giorgia Graells"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: "template.docx"
---

```{r setup, include=FALSE, echo=FALSE, comment=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)

```

#### Introduction

##### objectives

The aims of this study are: 1. Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2. identify how urbanization affects those bird assembles, 3. Evaluate iconic bird species habitat ocupation, and 4. describe bird behavior in those habitats



#### Metodology

##### Study area

Study area comprehends
Six habitats were identify in coastal urban areas

##### Bird surveys

##### Environmental variables

##### Seasonal GLMM

Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites. We tested a model where seasonality has a interacttion with the habitats defined in this research .

##### Occupancy modelling

##### Bird comunnity

Bird community was analysed by ordination methods with vegan package in R

1. Hacer una descripcion del ensamble de especies (unidas las temporadas) y representar con un NMDS, ANOSIM y SIMPER.
Se utiliz贸 las abundancias corregidas por ocupancia, lo que se obtiene corriendo los modelos de ocupancia para cada especie.

Mostrar la comparacio贸n entre natural y urbano.
Sumar Envfit

2. Realizar un mapa dde probabilidad de presencia para especies ic贸nicas 1-100%

3. Grafficar las barras de comportamiento para las mismas espcies ic贸nicas



#### Results

0. El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia

```{r tabla1}
#Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0


```

